Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by the Galaxy Cluster Abell 2744

### 2015-05-18 snTomas.tex
red text waiting for clarification of host galaxy mass from AM

\change{To measure the stellar mass of the host galaxy
we use Eq. 8 of \citet{Taylor:2011}, which relates the rest-frame
(g-i) color and i-band luminosity to the total stellar mass. To derive
these values, we fixed the redshift at $z=1.3457$ and repeated the SED
fitting using BPZ. From the best-fit SED we extracted rest-frame
optical magnitudes, and corrected them for lensing using a
magnification factor of $\mu=2.0$ -- a value that we will derive from
the SN itself in Section~\ref{sec:DistanceAndMagnification}.  From
this we determine the host galaxy mass to be $10^{10.1}$ \Msun. }

@@

\change{
If we were to apply the correction to this sample, then the SN \tomas\
distance modulus would not be adjusted, because its host galaxy mass
(Section~\ref{sec:HostGalaxy}) is below 10$^{10}$ \Msun. Note that
there is some circularity here, as we used the SN magnification in
deriving the host galaxy mass, and now use the host mass to inform the
magnification.  However, changing the magnification value to $mu=2.5$
does not move the \tomas\ host mass above the mass step threshold, so
the circularity is not relevant in this case. Applying the
mass step correction across the entire control sample would lead to a
small adjustment of the inferred SN \tomas\ magnification, but it is $<5\%$
and therefore could not relieve the observed tension.}

>>>>

\change{To measure the stellar mass of the host galaxy
we use Eq. 8 of \citet{Taylor:2011}, which relates the rest-frame
(g-i) color and i-band luminosity to the total stellar mass. To derive
these values, we fixed the redshift at $z=1.3457$ and repeated the SED
fitting using BPZ. From the best-fit SED we extracted rest-frame
optical magnitudes, and corrected them for lensing using a
magnification factor of $\mu=2.0$ -- a value that we will derive from
the SN itself in Section~\ref{sec:DistanceAndMagnification}.  From
this we determine the host galaxy mass to be 
\changeR{$10^{9}$ \Msun.} }

@@

\change{
If we were to apply the correction to this sample, then the SN \tomas\
distance modulus would not be adjusted, because its host galaxy mass
(Section~\ref{sec:HostGalaxy}) is \changeR{below} 10$^{10}$ \Msun. Note that
there is some circularity here, as we used the SN magnification in
deriving the host galaxy mass, and now use the host mass to inform the
magnification.  However, changing the magnification value to $mu=2.5$
\changeR{does not move the \tomas\ host mass above the mass} step threshold, so
the circularity is not relevant in this case. Applying the
mass step correction across the entire control sample would lead to a
small adjustment of the inferred SN \tomas\ magnification, but it is $<5\%$
and therefore could not relieve the observed tension.}
